Supplementary Analyses

### 2023-02-06 drafting_supplementary_analysis.Rmd
H2 all done (I think)

# H1 Gender Differences

## Internalization

@@

# x <- df[which(df$sex3=="male"|df$sex3=="female"),]
# x$sex3 <- droplevels(x$sex3)
# x <- x %>% group_by(country_name) %>% do(data = (.)) %>% with( set_names(data, country_name) )
# 
# #### identify countries with small samples
# male_length <- function(x){sum(x$sex3=='male')}
# males <- lapply(x, male_length)
# female_length <- function(x){sum(x$sex3=='female')}
# females <- lapply(x, female_length)
# names(females)
# 
# #### generate a vector containing all countries with less than 10 observations for either males or females ####
# exclusions <- c(names(males[males<2]),
#   names(females[females<2]))
# 
# #### re-load ungrouped data ####
# x <- df[which(df$sex3=="male"|df$sex3=="female"),]
# x$sex3 <- droplevels(x$sex3)
# 
# # and remove missing again
# sum(is.na(x$moral_identity_symbolic))
# x <- x[which(is.na(x$moral_identity_symbolic)==FALSE),]
# 
# #### Filter out any countries to be excluded ####
# x <- subset(x, !(country_name %in% exclusions))
# 
# df1 <- x
# 
# df1_male <- df1[which(df1$sex3=="male"),]
# df1_female <- df1[which(df1$sex3=="female"),]
# 
# internal_mean_sd <- function(x){
#   z <- x
#   z$mean <- mean(z$moral_identity_symbolic, na.rm=T)
#   z$sd <- sd(z$moral_identity_symbolic, na.rm=T)
#   z
# }
# 
# 
# df1 <- rbind.data.frame(
#   internal_mean_sd(df1_female),
#   internal_mean_sd(df1_male)
# )
# 
# df1$sex3 <- dplyr::recode(df1$sex3
#                            , "male" = "Male"
#                            , "female" = "Female")
# 
# g1 <- ggplot(df1,aes(x=sex3,y=moral_identity_symbolic))+
#   #geom_jitter(height = .1, width = .1, size=.0001, color="gray") +
#   geom_jitter(shape=16, position=position_jitter(height = .5, width = .45), size=.1, color="darkgrey")+
#   geom_violin(fill = NA) +
#   #ggforce::geom_sina(size=.01)+
#   # geom_sina(shape=16
#   #           , position=position_jitter(height=.25,width=0)
#   #           , size=.000001
#   #           , color="dark grey"
#   #           ,jitter_y=F
#   # )+
#   geom_boxplot(width=0.1, outlier.shape = NA, color='grey')+
#   geom_errorbar(aes(ymin=mean-sd, ymax=mean+sd), width=.06,
#                 position=position_dodge(0.05), color="#5a5a5a")+
#   stat_summary(fun=mean, geom="point", shape=16, size=.5)+
#   # stat_summary(geom = "linerange",
#   #   fun.data = mean_sdl,
#   #   fun.args = list(mult = 1),
#   #   colour = "black"
#   # )+
#   xlab("Gender")+
#   ylab("Internalization")+
#   facet_wrap(~df1$ISO3, ncol = 9 )+
#   #geom_jitter(shape=16, position=position_jitter(height = .5, width = .45), size=.01, color="dark grey")
#   theme_bw() +
#   theme(panel.border = element_blank(),
#         axis.line = element_line(size = .2),
#         strip.background  = element_blank(),
#         panel.grid = element_blank(),
#         plot.title=element_text(#family="Times",
#           size=12
#         ),
#         #legend.position="right",
#         legend.text=element_text(#family="Times",
#           size=8
#         ),
#         legend.title=element_text(#family="Times",
#           size=10
#         ),
#         axis.text=element_text(#family="Times",
#           colour = "black",
#           size=8
#         ),
#         axis.ticks.x = element_blank(),
#         axis.title=element_text(#family="Times",
#           size=12
#         ),
#         strip.text=element_text(#family = "Times",
#           size = 12
#         ),
#         # strip.background = element_rect(fill = "white"),
#         legend.position="none")
# 
# #g1
# 
# ggsave("plots/symbolization.png", g1, width = 40, height = 25, units = "in", dpi = 300)
#g2
```

@@

>>>>

# Gender
## Internalization

@@

# x <- df[which(df$sex3=="male"|df$sex3=="female"),]
# x$sex3 <- droplevels(x$sex3)
# x <- x %>% group_by(country_name) %>% do(data = (.)) %>% with( set_names(data, country_name) )
# 
# #### identify countries with small samples
# male_length <- function(x){sum(x$sex3=='male')}
# males <- lapply(x, male_length)
# female_length <- function(x){sum(x$sex3=='female')}
# females <- lapply(x, female_length)
# names(females)
# 
# #### generate a vector containing all countries with less than 10 observations for either males or females ####
# exclusions <- c(names(males[males<2]),
#   names(females[females<2]))
# 
# #### re-load ungrouped data ####
# x <- df[which(df$sex3=="male"|df$sex3=="female"),]
# x$sex3 <- droplevels(x$sex3)
# 
# # and remove missing again
# sum(is.na(x$moral_identity_symbolic))
# x <- x[which(is.na(x$moral_identity_symbolic)==FALSE),]
# 
# #### Filter out any countries to be excluded ####
# x <- subset(x, !(country_name %in% exclusions))
# 
# df1 <- x
# 
# df1_male <- df1[which(df1$sex3=="male"),]
# df1_female <- df1[which(df1$sex3=="female"),]
# 
# internal_mean_sd <- function(x){
#   z <- x
#   z$mean <- mean(z$moral_identity_symbolic, na.rm=T)
#   z$sd <- sd(z$moral_identity_symbolic, na.rm=T)
#   z
# }
# 
# 
# df1 <- rbind.data.frame(
#   internal_mean_sd(df1_female),
#   internal_mean_sd(df1_male)
# )
# 
# df1$sex3 <- dplyr::recode(df1$sex3
#                            , "male" = "Male"
#                            , "female" = "Female")
# 
# g1 <- ggplot(df1,aes(x=sex3,y=moral_identity_symbolic))+
#   #geom_jitter(height = .1, width = .1, size=.0001, color="gray") +
#   geom_jitter(shape=16, position=position_jitter(height = .5, width = .45), size=.1, color="darkgrey")+
#   geom_violin(fill = NA) +
#   #ggforce::geom_sina(size=.01)+
#   # geom_sina(shape=16
#   #           , position=position_jitter(height=.25,width=0)
#   #           , size=.000001
#   #           , color="dark grey"
#   #           ,jitter_y=F
#   # )+
#   geom_boxplot(width=0.1, outlier.shape = NA, color='grey')+
#   geom_errorbar(aes(ymin=mean-sd, ymax=mean+sd), width=.06,
#                 position=position_dodge(0.05), color="#5a5a5a")+
#   stat_summary(fun=mean, geom="point", shape=16, size=.5)+
#   # stat_summary(geom = "linerange",
#   #   fun.data = mean_sdl,
#   #   fun.args = list(mult = 1),
#   #   colour = "black"
#   # )+
#   xlab("Gender")+
#   ylab("Symbolization")+
#   facet_wrap(~df1$ISO3, ncol = 9 )+
#   #geom_jitter(shape=16, position=position_jitter(height = .5, width = .45), size=.01, color="dark grey")
#   theme_bw() +
#   theme(panel.border = element_blank(),
#         axis.line = element_line(size = .2),
#         strip.background  = element_blank(),
#         panel.grid = element_blank(),
#         plot.title=element_text(#family="Times",
#           size=12
#         ),
#         #legend.position="right",
#         legend.text=element_text(#family="Times",
#           size=8
#         ),
#         legend.title=element_text(#family="Times",
#           size=10
#         ),
#         axis.text=element_text(#family="Times",
#           colour = "black",
#           size=8
#         ),
#         axis.ticks.x = element_blank(),
#         axis.title=element_text(#family="Times",
#           size=12
#         ),
#         strip.text=element_text(#family = "Times",
#           size = 12
#         ),
#         # strip.background = element_rect(fill = "white"),
#         legend.position="none")
# 
# #g1
# 
# ggsave("plots/symbolization.png", g1, width = 40, height = 25, units = "in", dpi = 300)
# #g2
```

@@

# Age

```{r}
rm(list = ls())
#source("set_up_data_calculate_means.R")
load("data/data_with_means.RData")

## Age & Internalization

x <- df
x <- x[which(is.na(x$moral_identity_internal)==FALSE),]
x <- x[which(is.na(x$age)==FALSE),]
#### group by country for analysis ####
x <- x %>% group_by(country_name) %>% do(data = (.)) %>% with( set_names(data, country_name) )

exclusions <- names(total_Ns)[which(total_Ns<3)]
x <- df
x <- x[which(is.na(x$moral_identity_internal)==FALSE),]
x <- x[which(is.na(x$age)==FALSE),]
x <- subset(x, !(country_name %in% exclusions))

x <- x %>% group_by(country_name) %>% do(data = (.)) %>% with( set_names(data, country_name) )

cor_fun <- function(x){
  cor.test(x$moral_identity_symbolic,x$age)
}
all_cor_tests <- lapply(x, cor_fun)

all_cor_rs <- function(c){
  c$estimate
}
rs_for_table <- lapply(all_cor_tests, all_cor_rs)
all_cor_ps <- function(c){
  c$estimate
}
ps_for_table <- lapply(all_cor_tests, all_cor_ps)
ps_output_for_table <- lapply((lapply(all_cor_tests, all_cor_ps)), ps)
Ns_for_table <- lapply(x, N_fun)

means_INT_fun <- function(x){
  mean(x$moral_identity_internal)
}
mean_int_for_table <- lapply(x, means_INT_fun)
sd_INT_fun <- function(x){
  sd(x$moral_identity_internal)
}
sd_int_for_table <- lapply(x, sd_INT_fun)

means_age_fun <- function(x){
  mean(x$age)
}
mean_age_for_table <- lapply(x, means_age_fun)
sd_age_fun <- function(x){
  sd(x$age)
}
sd_age_for_table <- lapply(x, sd_age_fun)

test <- 
  cbind.data.frame(
     round(do.call(rbind,mean_age_for_table),digits = 2)
    ,round(do.call(rbind,sd_age_for_table),digits = 2)
    ,round(do.call(rbind,mean_int_for_table),digits = 2)
    ,round(do.call(rbind,sd_int_for_table),digits = 2)
    ,round(do.call(rbind, Ns_for_table))
    ,round(do.call(rbind, rs_for_table),digits=3)
    ,do.call(rbind, ps_output_for_table)
    )

test <- `colnames<-`(test, c("mean age","SD age","mean internalization", "SD internalization","N", "r","p"))
test

sum(unlist(ps_for_table)<.05)

test1 <- subset(test, p < .05)
test1

total_sig <- length(test1$`mean age`)

neg <- sum(test1$r <0 )
pos <- sum(test1$r>0)

x <- df
x <- x[which(is.na(x$moral_identity_internal)==FALSE),]
x <- x[which(is.na(x$age)==FALSE),]

x <- x %>% group_by(country_name) %>% do(data = (.)) %>% with( set_names(data, country_name) )

P_R <- x$`Puerto Rico`
P_R <- 
  `rownames<-`(
    `colnames<-`(
      as.data.frame(
        rbind(
          # c("mean F","SD F","mean M", "SD M", "t","df","p","d")
          # ,
          c(
            round(mean(P_R$age),digits=2)
            ,round(sd(P_R$age),digits=2)
            ,round(mean(P_R$moral_identity_internal),digits=2)
            ,round(sd(P_R$moral_identity_internal),digits=2)
            ,length(P_R$moral_identity_internal)
            ,"-"
            ,"-"))),
      c("mean age","SD age","mean internalization", "SD internalization","N", "r","p"))
    ,c("Puerto Rico"))

test <- rbind(test[1:49,],P_R,test[50:length(test$p),])
test <- test[order(rownames(test) ),]

apa_table(
  test
  , align = c("l", "l", "c", "c", "c", "c", "c", "c", "c", "c")
  , caption = "Correlation between Age and Internalization for each Country"
  , note = "* = sig. at p < .05; ** = sig. at p < .001")

## Age & Symbolization

x <- df
x <- x[which(is.na(x$moral_identity_symbolic)==FALSE),]
x <- x[which(is.na(x$age)==FALSE),]
#### group by country for analysis ####
x <- x %>% group_by(country_name) %>% do(data = (.)) %>% with( set_names(data, country_name) )

exclusions <- names(total_Ns)[which(total_Ns<3)]
x <- df
x <- x[which(is.na(x$moral_identity_symbolic)==FALSE),]
x <- x[which(is.na(x$age)==FALSE),]
x <- subset(x, !(country_name %in% exclusions))

x <- x %>% group_by(country_name) %>% do(data = (.)) %>% with( set_names(data, country_name) )

cor_fun <- function(x){
  cor.test(x$moral_identity_symbolic,x$age)
}
all_cor_tests <- lapply(x, cor_fun)

all_cor_rs <- function(c){
  c$estimate
}
rs_for_table <- lapply(all_cor_tests, all_cor_rs)
all_cor_ps <- function(c){
  c$estimate
}
ps_for_table <- lapply(all_cor_tests, all_cor_ps)
ps_output_for_table <- lapply((lapply(all_cor_tests, all_cor_ps)), ps)
Ns_for_table <- lapply(x, N_fun)

means_INT_fun <- function(x){
  mean(x$moral_identity_symbolic)
}
mean_int_for_table <- lapply(x, means_INT_fun)
sd_INT_fun <- function(x){
  sd(x$moral_identity_symbolic)
}
sd_int_for_table <- lapply(x, sd_INT_fun)

means_age_fun <- function(x){
  mean(x$age)
}
mean_age_for_table <- lapply(x, means_age_fun)
sd_age_fun <- function(x){
  sd(x$age)
}
sd_age_for_table <- lapply(x, sd_age_fun)

test <- 
  cbind.data.frame(
     round(do.call(rbind,mean_age_for_table),digits = 2)
    ,round(do.call(rbind,sd_age_for_table),digits = 2)
    ,round(do.call(rbind,mean_int_for_table),digits = 2)
    ,round(do.call(rbind,sd_int_for_table),digits = 2)
    ,round(do.call(rbind, Ns_for_table))
    ,round(do.call(rbind, rs_for_table),digits=3)
    ,do.call(rbind, ps_output_for_table)
    )

test <- `colnames<-`(test, c("mean age","SD age","mean symbolization", "SD symbolization","N", "r","p"))
test

sum(unlist(ps_for_table)<.05)

test1 <- subset(test, p < .05)
test1

total_sig <- length(test1$`mean age`)

neg <- sum(test1$r <0 )
pos <- sum(test1$r>0)

x <- df
x <- x[which(is.na(x$moral_identity_symbolic)==FALSE),]
x <- x[which(is.na(x$age)==FALSE),]

x <- x %>% group_by(country_name) %>% do(data = (.)) %>% with( set_names(data, country_name) )

P_R <- x$`Puerto Rico`
P_R <- 
  `rownames<-`(
    `colnames<-`(
      as.data.frame(
        rbind(
          # c("mean F","SD F","mean M", "SD M", "t","df","p","d")
          # ,
          c(
             round(mean(P_R$age),digits=2)
            ,round(sd(P_R$age),digits=2)
            ,round(mean(P_R$moral_identity_symbolic),digits=2)
            ,round(sd(P_R$moral_identity_symbolic),digits=2)
            ,length(P_R$moral_identity_symbolic)
            ,"-"
            ,"-"))),
      c("mean age","SD age","mean symbolization", "SD symbolization","N", "r","p"))
    ,c("Puerto Rico"))

test <- rbind(test[1:49,],P_R,test[50:length(test$p),])
test <- test[order(rownames(test) ),]

apa_table(
  test
  , align = c("l", "l", "c", "c", "c", "c", "c", "c", "c", "c")
  , caption = "Correlation between Age and Symbolization for each Country"
  , note = "* = sig. at p < .05; ** = sig. at p < .001")
